Approximation as Differentiation notes

### 2025-03-10 notes/sec/grothendieck.tex
Indexing component of lambda is an iso by Cartesian closure of Set.
Inline g.

\begin{enumerate}
\item $[X, Y]$ to be the object in $\Fam(C)$ with $\idx{[X,Y]} = \Fam(C)(X,Y)$ and $\faml{[X, Y]}(f) =
\prod_{\idx{X}}\reindex{\faml{Y}}{\idx{f}}$ for every $f: X \to Y$.
\item The family of isomorphisms $\lambda_{X,Y,Z}$ (natural in $X$) sending any $f: X \times Y \to Z$ to
$\lambda_{X,Y,Z}(f): X \to [Y, Z]$ with:
\begin{itemize}
\item $\idx{\lambda}_{X,Y,Z}(f)(x) = g$ where $\idx{g} = \idx{f} \comp (x, -): \idx{Y} \to \idx{Z}$ and
$\faml{g} = \reindex{\faml{f}}{(x,-)} \comp \inj_{\faml{Y}}: \faml{Y} \to \reindex{\faml{Z}}{\idx{g}}$ where $\inj_{\faml{Y}}:
\faml{Y} \to \const_{\idx{Y}}(\faml{X}_x) \biprod \faml{Y}$
\item $\faml{\lambda}_{X,Y,Z}(f)(x) = \lambda_{\prod_{\idx{Y}}}(\reindex{\faml{f}}{(x,-)} \comp \inj_{\faml{X}_x}:
\const_{\idx{Y}}(\faml{X}_x) \to \reindex{\faml{Z}}{\idx{f}})$ where $\inj_{\faml{X}_x}: \const_{\idx{Y}}(\faml{X}_x)
\to \const_{\idx{Y}}(\faml{X}_x) \biprod \faml{Y}$
\end{itemize}
\item The family of morphisms $\eval_{X,Y}: [X, Y] \times X \to Y$ in $\Fam(C)$ with
\begin{itemize}
\item $\idx{\eval}_{X,Y}(f, x) = \idx{f}(x)$
\item $\faml{\eval}_{X,Y}(f, x) = \coprodM{{\eval_{\prod}}_x}{\faml{f}_x}:
\prod_{\idx{X}}\reindex{\faml{Y}}{\idx{f}} \biprod \faml{X}_x \to \faml{Y}_{\idx{f}(x)}$
\end{itemize}
using $\coprodM{-}{-}$ to denote coproduct of morphisms.
\end{enumerate}

@@

\begin{enumerate}
\item $\idx{\lambda}_{X,Y,Z}$ is an isomorphism by the ismorphism of $\idx{X} \times \idx{Y} \to \idx{Z}$ and
$\idx{X} \to \idx{Y} \to \idx{Z}$. For $\faml{\lambda}_{X,Y,Z}$, define the family of functions
$\lambda^{-1}_{X,Y,Z}$ sending any $f: X \to [Y,Z]$ to $\lambda^{-1}_{X,Y,Z}(f): X \times Y \to Z$ with:
\begin{itemize}
\item $\idx{\lambda^{-1}}_{X,Y,Z}(f)(x,y) = \idx{g}(y)$ where $\idx{f}(x) = g$
\item $\faml{\lambda^{-1}}_{X,Y,Z}(f)(x,y) =$
\end{itemize}

>>>>

\begin{enumerate}
\item $[X, Y]$ to be the object in $\Fam(C)$ with $\idx{[X,Y]} = \Fam(C)(X,Y)$ and $\faml{[X, Y]}(f) =
\prod_{\idx{X}}\reindex{\faml{Y}}{\idx{f}}$ for every $f: X \to Y$.
\item The family of isomorphisms $\lambda_{X,Y,Z}$ (natural in $X$) sending any $f: X \times Y \to Z$ to
$\lambda_{X,Y,Z}(f): X \to [Y, Z]$ with:
\begin{itemize}
\item $\idx{\lambda}_{X,Y,Z}(f)(x) = (\idx{f} \comp (x, -), \reindex{\faml{f}}{(x,-)} \comp \inj_{\faml{Y}}):
Y \to Z$ where $\inj_{\faml{Y}}: \faml{Y} \to \const_{\idx{Y}}(\faml{X}_x) \biprod \faml{Y}$
\item $\faml{\lambda}_{X,Y,Z}(f)(x) = \lambda_{\prod_{\idx{Y}}}(\reindex{\faml{f}}{(x,-)} \comp \inj_{\faml{X}_x}:
\const_{\idx{Y}}(\faml{X}_x) \to \reindex{\faml{Z}}{\idx{f}})$ where $\inj_{\faml{X}_x}: \const_{\idx{Y}}(\faml{X}_x)
\to \const_{\idx{Y}}(\faml{X}_x) \biprod \faml{Y}$
\end{itemize}
\item The family of morphisms $\eval_{X,Y}: [X, Y] \times X \to Y$ in $\Fam(C)$ with
\begin{itemize}
\item $\idx{\eval}_{X,Y}(f, x) = \idx{f}(x)$
\item $\faml{\eval}_{X,Y}(f, x) = \coprodM{{\eval_{\prod}}_x}{\faml{f}_x}:
\prod_{\idx{X}}\reindex{\faml{Y}}{\idx{f}} \biprod \faml{X}_x \to \faml{Y}_{\idx{f}(x)}$
\end{itemize}
using $\coprodM{-}{-}$ to denote coproduct of morphisms.
\end{enumerate}

@@

\begin{enumerate}
\item $\idx{\lambda}_{X,Y,Z}$ is an isomorphism because $\idx{X} \times \idx{Y} \to \idx{Z} \iso \idx{X} \to
\idx{Y} \to \idx{Z}$. For $\faml{\lambda}_{X,Y,Z}$, define the following family of functions sending any $f: X
\to [Y,Z]$ to $\lambda^{-1}_{X,Y,Z}(f): X \times Y \to Z$ with:
\begin{itemize}
\item $\faml{\lambda^{-1}}_{X,Y,Z}(f)(x,y) = \faml{g}_y$ where $\idx{f}(x) = g$
\end{itemize}
